\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-25 Manuscript/Manuscript.tex
PUB

\clearpage
\section{Results and discussion}

>>>>

\clearpage
\subsection{Support vector machines}
The basic idea of the support vector machines is to consider the input set \textbf{X} ($n\times P$, where n stands for the observations and p for the features) as an ensemble of n-points immersed in to a p-dimensional space. Furthermore each point is labelled only in two way \footnote{The approaches described here can be extended to a multiple classes problem as shown in \cite{james2013introduction}, however since in this work only two classes are allowed (habitable or not) this such implementation will not be reviewed}. Thus, with this representation, the classification problem is recast in to a partition of a hyperspace. The simple form by which an hyperspace can be partitioned is an hyperplane:

\begin{equation}
\beta_{0}+\beta_{1}x_{i1}+\beta_{1}x_{i2}+...+\beta_{p}x_{ip} > 0\quad if \quad y_{i}=1
\end{equation}
\begin{equation}
\beta_{0}+\beta_{1}x_{i1}+\beta_{1}x_{i2}+...+\beta_{p}x_{ip} < 0\quad if \quad y_{i}=0
\end{equation}

The problem now is how to choose the hyperplane: this is a first discriminant between the SVM methods, moreover anything guarantee that the boundary is linear and thus a simple hypoerplane can be used; this is a second discriminant between the SVM methods. It is worth nothing that in principle one can introduce a further dimension, as shown in Fig \ref{Kernel_methods} in order to have a linear hyperplane: this is the idea of the kernel methods (further details are provided in \cite{james2013introduction,marsland2015machine}. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.9\textwidth]{Pic/kernel_trick.png}
\caption{The trick of the kernel methods: introducing an extra dimension they transform a non-linear boundary in to a linear one.  Image taken from \cite{kernel}}
\label{Kernel_methods}
\end{center}
\end{figure}

\section{Results and discussion}
